\huge A Usability Evaluation of Tor Launcher

### 2016-11-10 pets2017-paper/pets2017-paper.tex
initialize tables for demographics data in appendix

\section{Prescreening Survey Responses}
\label{prescreening-responses}
We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing. We did not use these self-reported answers to influence any process of our testing. We show the responses from the particpants that we chose.

We suspect that participants answered dishonestly in hopes of appearing more technically fluent. We know this because some reported that they were familiar a term that did not exist (x.511 certificates). We inserted this fictional term specifically to detect this. Here are our participants' self-reported familiarity with technical terms: \\

{\color {red} MAKE A TABLE HERE} \\

Participants' self-reported use of security tools. We assume that self-reported use is the upper bound of how many participants have used these security tools. Here are our participants' self-reported use of security tools:\\

{\color {red} MAKE A TABLE HERE}

>>>>

{\color {red}
\section{Prescreening Survey Responses}
\label{prescreening-responses}
We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing. We show the responses from the particpants that we chose.

\begin{table}[h]
\centering
\begin{tabular}{l r r}
& Familiarity\\
\noalign{\hrule}
Malware & 00/00\\
Proxy services & 00/00\\
Phishing & 00/00\\
SSL & 00/00\\
X.511 certificates & 00/00\\
Tor & 00/00\\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-tech}
\end{table}

We suspect that participants answered dishonestly in hopes of appearing more technically fluent. We know this because some reported that they were familiar a term that did not exist (x.511 certificates). We inserted this fictional term specifically to detect this.

\begin{table*}[h]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{}\\
& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily}\\
\noalign{\hrule}
HTTPS on web pages& 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Proxies or censorship circumvention tools & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Virtual private networks (VPNs) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
File or disk encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Anonymity systems (e.g. Tor) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Email encryption (e.g. PGP) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Instant messaging encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
Voice communication encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-software}
\end{table*}

We assume that self-reported use is the upper bound of how many participants have used these security tools.
}
